### 2014-03-12 src/analysis.Rnw
Remove subsum graphs
update

@@

@@

For comparing between different techniques, we ran correlation analysis between the full mutation score,
and that produced by the reduction criteria. Further, we also collected the mean reduction, and the standard
deviation of the reduction across all the projects for both randoop and original. These statistics are provided below.
\subsection{Sampling Criteria}
% We have power, element, kind(O/R), and MuRed, MuRedSD, R^2
\subsubsection{x\% selection}
<<xpercentunit>>=
sel.colnames <- c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier')
new.colnames <- c('operator', 'r^2',      'm.red',            'm.sd',         'num',    'B*')
stats.xp <- subset(stats.df, grepl('^(r|rr|rc)[.]', operator)) # We are ignoring ceil here. add rc if needed.

o.stats.sel.xp <- subset(o.f(stats.xp), select=sel.colnames)
r.stats.sel.xp <- subset(r.f(stats.xp), select=sel.colnames)
stats.rest <- subset(stats.df, !grepl('^(r|rr|rc)[.]', operator))
colnames(o.stats.sel.xp) <- new.colnames
colnames(r.stats.sel.xp) <- new.colnames
@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(subset(o.stats.sel.xp, grepl('^r[.]', operator)), caption='Original', label='table:rando', main='Original'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(subset(r.stats.sel.xp, grepl('^r[.]', operator)), caption='Randoop', label='table:randr', main='Randoop'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The round(x)\% random selection criteria results.}
\label{tbl:xsel}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(subset(o.stats.sel.xp, grepl('^rr[.]', operator)), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(subset(r.stats.sel.xp, grepl('^rr[.]', operator)), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The sample(x)\% random selection criteria results.}
\label{tbl:xsel2}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(subset(o.stats.sel.xp, grepl('^rc[.]', operator)), caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(subset(r.stats.sel.xp, grepl('^rc[.]', operator)), caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The ceil(x)\% random selection criteria results.}
\label{tbl:xsel2}
\end{table*}

@@

For operator selection, we approximated the operators as far as possible from the research works into the operators exposed by PIT. The results of this are provided in Table~\ref{tbl:opsel}. The subsumption graphs are provided in Figure~\ref{fig:subsumptiono}
% TODO : Check if this makes sense.
\begin{figure*}[t]
\includegraphics[totalheight=6cm]{fig/original.pdf}
\caption{Subsumption Original}
\label{fig:subsumptiono}
\end{figure*}

>>>>

<<xpercentunit>>=
sel.colnames <- c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier')
new.colnames <- c('operator', 'r^2',      'm.red',            'm.sd',         'num',    'B*')
stats.xp <- subset(stats.df, grepl('^(r|rr|rc)[.]', operator)) # We are ignoring ceil here. add rc if needed.

o.stats.sel.xp <- subset(o.f(stats.xp), select=sel.colnames)
r.stats.sel.xp <- subset(r.f(stats.xp), select=sel.colnames)
stats.rest <- subset(stats.df, !grepl('^(r|rr|rc)[.]', operator))
colnames(o.stats.sel.xp) <- new.colnames
colnames(r.stats.sel.xp) <- new.colnames

o.stats.sel.xp.sample <- subset(o.stats.sel.xp, grepl('^rr[.]', operator))
r.stats.sel.xp.sample <- subset(r.stats.sel.xp, grepl('^rr[.]', operator))
o.stats.sel.xp.sample$operator <- gsub('rr[.]1x','1/', subset(o.stats.sel.xp, grepl('^rr[.]', operator))$operator)
r.stats.sel.xp.sample$operator  <- gsub('rr[.]1x','1/', subset(r.stats.sel.xp, grepl('^rr[.]', operator))$operator)

o.stats.sel.xp.round <- subset(o.stats.sel.xp, grepl('^r[.]', operator))
r.stats.sel.xp.round <- subset(r.stats.sel.xp, grepl('^r[.]', operator))
o.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', subset(o.stats.sel.xp, grepl('^r[.]', operator))$operator)
r.stats.sel.xp.round$operator  <- gsub('r[.]1x','1/', subset(r.stats.sel.xp, grepl('^r[.]', operator))$operator)

o.stats.sel.xp.ceil <- subset(o.stats.sel.xp, grepl('^rc[.]', operator))
r.stats.sel.xp.ceil <- subset(r.stats.sel.xp, grepl('^rc[.]', operator))
o.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', subset(o.stats.sel.xp, grepl('^rc[.]', operator))$operator)
r.stats.sel.xp.ceil$operator  <- gsub('rc[.]1x','1/', subset(r.stats.sel.xp, grepl('^rc[.]', operator))$operator)

@
\subsubsection{x\% selection}
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.xp.sample, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.xp.sample, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The sample(x)\% random selection criteria results.}
\label{tbl:xselsample}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.xp.round, caption='Original', label='table:rando', main='Original'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.xp.round, caption='Randoop', label='table:randr', main='Randoop'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The round(x)\% random selection criteria results.}
\label{tbl:xselround}
\end{table*}

\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.xp.ceil, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.xp.ceil, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The ceil(x)\% random selection criteria results.}
\label{tbl:xselceil}
\end{table*}

@@

Our results for x\% sampling over program elements are given in Table~\ref{tbl:xselsample}. The result of
its variation, using \textit{round(sample)} is given in Table~\ref{tbl:xselround}. The result of using \textit{ceil(sample)}
is given in Table~\ref{tbl:xselceil}.

@@

For comparing between different techniques, we ran correlation analysis between the full mutation score,
and that produced by the reduction criteria. Further, we also collected the mean reduction, and the standard
deviation of the reduction across all the projects for both randoop and original. These statistics are provided below.
\subsection{Sampling Criteria}

@@

For operator selection, we approximated the operators as far as possible from the research works into the operators exposed by PIT. The results of this are provided in Table~\ref{tbl:opsel}.
% The subsumption graphs are provided in Figure~\ref{fig:subsumptiono}
% TODO : Check if this makes sense.
%\begin{figure*}[t]
%\includegraphics[totalheight=6cm]{fig/original.pdf}
%\caption{Subsumption Original}
%\label{fig:subsumptiono}
%\end{figure*}
